### 2014-09-12 A1/writeup/writeup.tex
Updated things

Figure \ref{fig:result} contains our primary findings. After analyzing the coefficient on uniqueness for each of the 300 product-level logistic regressions, we find that the average coefficient on uniqueness to be $-1.43$ ($p < 10^{-15}$). This is an indication that, based on our uniqueness and helpfulness metrics, lexical uniqueness has a negative influence on helpful voting.

@@

(WE SHOULD RUN REGRESSIONS WITH DEVIANCE FROM AVERAGE REVIEW SCORE -AND- UNIQUENESS AS PREDICTORS FOR REVIEW HELPFULNESS. IF SOMEONE WANTED TO ADD THIS AND MAYBE ANOTHER GRAPH, THAT WOULD BE REALLY GREAT. ESSENTIALLY, RUN A REGRESSION WITH BOTH HELPFULNESS -AND- REVIEW DEVIANCE FROM MEAN REVIEW SCORE. THIS WILL INVOLVE CHANGING THE OUTPUT OF THE PYTHON SCRIPT VERY SLIGHTLY, SO THAT THIS DATA IS WRITTEN PROPERLY INTO THE OUTPUT CSVs.)

>>>>

Figure \ref{fig:result} contains our primary findings. After analyzing the coefficient on uniqueness for each of the 300 product-level logistic regressions, we find that the average coefficient on uniqueness to be $-1.52$ ($p < 10^{-15}$). This is an indication that, based on our uniqueness and helpfulness metrics, lexical uniqueness has a negative influence on helpful voting.

@@

(PARAGRAPH ABOUT SENTIMENT/SCORING) $-1.50$ ($p < 10^{-15}$)
